---
title: "Overview of TRI's GA4 Data Analysis"
subtitle: "Analysis over a 28-day observation window"
author: "Ashley Lee"
date: today
format:
  revealjs:
    theme: solarized
    transition: slide
    slide-number: true
    chalkboard: false
    code-fold: true
    self-contained: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(dplyr)
library(ggplot2)
library(scales)
library(plotly)
library(DT)
library(tidyr)
library(forcats)
library(here)


ga4_events_28d <- readRDS(here::here("../../../IBM 6530/W10-Dashboards Assignment/M10-Website/shiny-app/ga4_events_28d.rds"))

ga4_events_28d <- ga4_events_28d |>
  mutate(
    event_date = as.Date(event_date, format = "%Y%m%d"),
    source = ifelse(is.na(source) | source == "", "Unknown", source),
    medium = ifelse(is.na(medium) | medium == "", "Unknown", medium),
    device_category = ifelse(is.na(device_category) | device_category == "", "Unknown", device_category),
    country = ifelse(is.na(country) | country == "", "Unknown", country)
  )

ga4_events_28d <- ga4_events_28d |>
  mutate(
    user_key = dplyr::case_when(
      !is.na(user_pseudo_id) ~ paste0("uid_", user_pseudo_id),
      TRUE ~ paste("proxy", device_category, country, sep = "_")
    )
  ) |>
  group_by(user_key) |>
  arrange(event_ts, .by_group = TRUE) |>
  mutate(
    time_diff_mins = as.numeric(difftime(event_ts, lag(event_ts), units = "mins")),
    new_session = ifelse(is.na(time_diff_mins) | time_diff_mins > 30, 1L, 0L),
    session_seq = cumsum(new_session)
  ) |>
  ungroup()

df_sessions <- ga4_events_28d |>
  group_by(user_key, session_seq) |>
  summarise(
    session_date          = as.Date(min(event_ts, na.rm = TRUE)),
    device_category       = first(device_category),
    traffic_source        = first(source),
    medium                = first(medium),
    page_views            = sum(event_name == "page_view", na.rm = TRUE),
    training_page_view    = as.integer(any(event_name == "training_page_view")),
    is_booking_conversion = as.integer(any(event_name == "checkout_started")),
    is_donation_conversion= as.integer(any(event_name == "donate_button_click")),
    is_email_conversion   = as.integer(any(event_name == "newsletter_signup")),
    engagement_sec        = as.numeric(difftime(max(event_ts), min(event_ts), units = "secs")),
    .groups = "drop"
  ) |>
  filter(page_views > 0, page_views <= 50) |>
  mutate(
    engagement_sec = ifelse(is.na(engagement_sec) | !is.finite(engagement_sec), 0, engagement_sec),
    is_any_conversion = as.integer(is_booking_conversion | is_donation_conversion | is_email_conversion),
    page_view_bucket = factor(
      case_when(
        page_views == 1  ~ "1 page",
        page_views <= 3  ~ "2–3 pages",
        page_views <= 6  ~ "4–6 pages",
        page_views <= 15 ~ "7–15 pages",
        TRUE             ~ "16–50 pages"
      ),
      levels = c("1 page", "2–3 pages", "4–6 pages", "7–15 pages", "16–50 pages")
    )
  )
```

## About This Analysis {background-color="#1a1a2e"}

::: incremental
-   **Client:** Trauma Resource Institute (TRI) — a nonprofit offering trauma-informed trainings for clinicians and communities
-   **Data:** 28-day obeservation window GA4 event-level data (\~3,700 sessions)
-   **Analysis Goal:** Understand what drives users from a page view to a booking conversion, and implement strategies to improve bounce rates
-   **Tools:** R, Quarto, SQL, BigQuery, GA4
:::

## Analytical Observation Goals: {background-color="#1a1a2e"}

> -   Improve conversion rates across the TRI site.
>
> -   Do users who view more pages convert at higher rates?
>
> -   Which traffic sources and devices drive the most engaged visitors?

------------------------------------------------------------------------

## Key Metrics {.smaller}

```{r}
tibble(
  Metric = c("Total Sessions", "Booking Conversions", 
             "Conversion Rate", "Avg Page Views", "Median Engagement"),
  Value = c(
    comma(nrow(df_sessions)),
    comma(sum(df_sessions$is_booking_conversion)),
    percent(mean(df_sessions$is_booking_conversion), accuracy = 0.01),
    round(mean(df_sessions$page_views), 1),
    paste0(round(median(df_sessions$engagement_sec), 0), " sec")
  )
) |>
  DT::datatable(rownames = FALSE, options = list(dom = "t", paging = FALSE))
```

------------------------------------------------------------------------

## Finding 1: Most Users Never Go Beyond 1 Page {.smaller}

```{r}
threshold_data <- df_sessions |>
  count(page_view_bucket) |>
  mutate(pct = n / sum(n))

ggplot(threshold_data, aes(x = page_view_bucket, y = n)) +
  geom_col(fill = "#2F80ED", width = 0.6) +
  geom_text(aes(label = paste0(comma(n), "\n(", percent(pct, accuracy = 0.1), ")")),
            vjust = -0.3, size = 3.5, fontface = "bold") +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Session Distribution by Page View Depth",
       x = "Page View Bucket", y = "Sessions",
       caption = "Source: TRI GA4 data · 28-day window") +
  theme_minimal(base_size = 13) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(face = "bold"))
```

------------------------------------------------------------------------

## Finding 2: Conversion Rises Sharply at 4+ Pages {.smaller}

```{r}
cvr_data <- df_sessions |>
  group_by(page_view_bucket) |>
  summarise(
    sessions = n(),
    conversions = sum(is_booking_conversion),
    cvr = conversions / sessions,
    .groups = "drop"
  )

baseline <- mean(df_sessions$is_booking_conversion)

ggplot(cvr_data, aes(x = page_view_bucket, y = cvr,
                     fill = cvr > baseline)) +
  geom_col(width = 0.6) +
  geom_hline(yintercept = baseline, linetype = "dashed", color = "gray50") +
  geom_text(aes(label = percent(cvr, accuracy = 0.1)),
            vjust = -0.4, size = 3.8, fontface = "bold") +
  scale_fill_manual(values = c("FALSE" = "#AAAAAA", "TRUE" = "#2F80ED"),
                    guide = "none") +
  scale_y_continuous(labels = percent_format(accuracy = 0.1),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Booking Conversion Rate by Page Depth",
       subtitle = paste0("Dashed line = baseline CVR (",
                         percent(baseline, accuracy = 0.01), ")"),
       x = "Page View Bucket", y = "Conversion Rate",
       caption = "Source: TRI GA4 data") +
  theme_minimal(base_size = 13) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(face = "bold"))
```

------------------------------------------------------------------------

## Finding 3: Device Breakdown {.smaller}

```{r}
device_data <- df_sessions |>
  group_by(device_category) |>
  summarise(
    sessions = n(),
    cvr = mean(is_booking_conversion),
    .groups = "drop"
  ) |>
  filter(!is.na(device_category))

ggplot(device_data, aes(x = fct_reorder(device_category, sessions), y = sessions, fill = device_category)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(comma(sessions), "\nCVR: ", percent(cvr, accuracy = 0.1))),
            hjust = -0.1, size = 3.5) +
  scale_fill_manual(values = c("desktop" = "#1a1a2e", "mobile" = "#2F80ED", "tablet" = "#90CAF9"),
                    guide = "none") +
  scale_x_discrete(labels = tools::toTitleCase) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.3))) +
  coord_flip() +
  labs(title = "Sessions & Conversion Rate by Device",
       x = NULL, y = "Sessions",
       caption = "Source: TRI GA4 data") +
  theme_minimal(base_size = 13) +
  theme(panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold"))
```

------------------------------------------------------------------------

## Finding 4: Top Traffic Sources {.smaller}

```{r}
source_data <- df_sessions |>
  group_by(traffic_source) |>
  summarise(
    sessions = n(),
    cvr = mean(is_booking_conversion),
    .groups = "drop"
  ) |>
  arrange(desc(sessions)) |>
  slice_head(n = 8)

ggplot(source_data, aes(x = fct_reorder(traffic_source, sessions), y = sessions)) +
  geom_col(fill = "#2F80ED", width = 0.6) +
  geom_text(aes(label = paste0(comma(sessions), " | CVR: ", percent(cvr, accuracy = 0.1))),
            hjust = -0.05, size = 3.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.4))) +
  coord_flip() +
  labs(title = "Top 8 Traffic Sources by Session Volume",
       x = NULL, y = "Sessions",
       caption = "Source: TRI GA4 data") +
  theme_minimal(base_size = 13) +
  theme(panel.grid.major.y = element_blank(),
        plot.title = element_text(face = "bold"))
```

------------------------------------------------------------------------

## Key Insights & Recommendations {background-color="#1a1a2e"}

::: incremental
-   **60% of sessions end after 1 page** — TRI's biggest opportunity is improving early-session engagement
-   **4+ page sessions convert 5–28x higher** — content depth = strong booking intent
-   **Mobile drives volume, Desktop drives conversions** — optimize mobile UX for conversion opportunities
-   **Training page views correlate with conversion** — promote training content [earlier]{.underline} in the funnel
:::

------------------------------------------------------------------------

# Thank You!

# 
