---
title: "Analytics Projects - TRI Specific"
subtitle: "Data analysis and interactive tools built with R, Shiny, and Quarto to support a year-long capstone initiative with the Trauma Resource Institute."
---

## Overview

This section showcases my applied analytics work using GA4 event-level data from the Trauma Resource Institute (TRI) — a nonprofit offering trauma-informed training programs for communities and healthcare professionals. 

Each project applies a different analytical tool to answer real marketing questions 
around user behavior, conversion optimization, and engagement.

---

## Quarto Dashboard — TRI Page View Analysis

An interactive Quarto dashboard analyzing whether users who view more pages are more
likely to convert. Includes conversion funnel breakdowns, session-level metrics, 
and key insights for nonprofit marketing strategy.

```{r}
#| echo: false
knitr::include_url("quarto-dashboard.html", height = "600px")
```

---

## Shiny App — TRI Conversion Analytics

A full Shiny application with global filters for date range, device, and traffic source. 
Features logistic regression odds ratios, random forest variable importance, and 
predicted booking probability curves.

[Launch Shiny App](https://ashleyxlee.shinyapps.io/msdm-project/){.btn .btn-primary target="_blank"}

---

## RevealJS Presentation — GA4 Data Analysis

A slide deck summarizing the full 28-day TRI GA4 analysis — covering session behavior, 
conversion rates by page depth, device breakdowns, and traffic source quality. 
Built with Quarto RevealJS.

```{r}
#| echo: false
knitr::include_url("portfolio_revealjs.html", height = "500px")
```
